Hierarchical Dispatching and Overriding

### 2017-09-19 NewVersion/sections/Auxiliary.tex
Last review for today
reply marco
refine
remove StaticInvocation
refine auxiliaries
fix
More proof.

@@

    \inferrule* [left=]
    { set1 = \; \{K\mid I <: K, \; K <: J\; $and$\; m \in \overrideSet(K, K) \} \\
        set2 = \; \{K\mid  J <: K \; $and$\; m \in \overrideSet(K, K) \} }
    {\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
                $prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
            \end{tabular}}\right.}

    \inferrule* [left=]
        { set = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
            m \in \overrideSet(K, J)  \} }
        {\mostSpecificOverride(m, I, J) = prune(set)}

    prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\}

    \inferrule* [left=]
    {   \interface{I}{I}{M}
        \\ J \in \overline{I} }
    {\ext(I, J) \marco{Is this ever used?}}

    \inferrule* [left=]
    {   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
        \kwoverride \; J \ldots \} }
    {m \in \overrideSet(I, J)}
    \end{mathpar}
    \caption{Auxiliary functions.}\label{fig:auxfunc}
\end{figure*}

@@

\subsection{$\canInstantiate$}
We use the auxilary function $\canInstantiate(I)$ to check whether an interface $I$ can be instantiated or not.
The algorithm is decribed below:
\begin{enumerate}
\item Suppose $\mostSpecific(m, I, I) = \overline{J}$, where $\overline{J}$ is a list of interfaces.
\item If $\forall J_i \in \overline{J}, if \mostSpecificOverride(m, I, J_i) = \{ K \} $ and $m$ in $K$ is not abstract, 
then $\canInstantiate(I) = true$, else $\canInstantiate(I) = false$.
\end{enumerate}

\subsection{$\mbodyStatic$}
The auxilary function $\mbodyStatic$ serves for method loopup for static method invocation. 
The brief description of the algorithm follows:
\begin{mathpar}
    \inferrule* [left=]
        {  %\mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J}{e_0}\ldots\}}
        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}

    \inferrule* [left=]
        {  %\mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J}\ldots\}}
        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
\end{mathpar}

>>>>

% $\begin{array}{l}
% \InTextDef{15ex}{
% \mBody(\m,\C_0)
% }{
% \override(\methods(\m),
% \tops(\m,\Cs))
% }\\
% \InTextWith{\metaVar{IT}(\C_0) =
% \ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_n}\\
% \hspace{1.2in}\oC\methods\ \cC \mbox{ and } \C\in\Cs \mbox{ if } \C_i\subtype\C, i\in 1..n

% \end{array}$

% \noindent The definition of $\mBody$ reconstructs the full set of supertypes $\Cs$ and then delegates the work to two other auxiliary functions:
%  $\tops(m,\Cs)$ and $\override(\method,\methods)$.

@@

    \inferrule* [left=]
    { originalIntfs = \; \{K \mid \subt{I}{K}, \; \subt{K}{J} \; \lor \; \subt{J}{K}, \; $and$\; m \in \overrideSet(K, K) \} }
    {\mostSpecific(m, I, J) = \prune(originalIntfs) }

    \inferrule* [left=]
        { overrideIntfs = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
            m \in \overrideSet(K, J)  \} }
        {\mostSpecificOverride(m, I, J) = \prune(overrideIntfs)}

    \prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\}

    % \inferrule* [left=]
    % {   \interface{I}{I}{M}
    %     \\ J \in \overline{I} }
    % {\ext(I, J) \marco{Is this ever used?} \yanlin{Previously used, new version not used.}}

    \inferrule* [left=]
    {   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
        \kwoverride \; J \ldots \} }
    {m \in \overrideSet(I, J)}

      \inferrule* [left=]
    {   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
        	\kwoverride \; I \ldots \} \\
        \kwinterface \; J \; \kwextends \; \overline{J} \; \{ I_e \; m(\overline{I_x} \; \overline{y}) \;
      	    \kwoverride \; J \ldots \} \\
    }
    {\canOverride(m, I, J)}
    \end{mathpar}
    \caption{Auxiliary functions.}\label{fig:auxfunc}
\end{figure*}

@@

\subsection{$\canInstantiate$}
We use the auxilary function $\canInstantiate(I)$ to check whether an interface $I$ can be instantiated or not.
The algorithm is decribed below:

$$\forall m, \forall J \in \mostSpecific(m, I, I), $$
\begin{enumerate}
\item For any $m$, suppose $\mostSpecific(m, I, I) = \overline{J}$, where $\overline{J}$ is a list of interfaces.
\item If $\forall J_i \in \overline{J}, if \mostSpecificOverride(m, I, J_i) = \{ K \} $ and $m$ in $K$ is not abstract, 
then $\canInstantiate(I) = true$, else $\canInstantiate(I) = false$.
\end{enumerate}

\begin{comment}
\subsection{$\mbodyStatic$}
The auxilary function $\mbodyStatic$ serves for method loopup for static method invocation. 
The brief description of the algorithm follows:
\begin{mathpar}
    \inferrule* [left=]
        {  %\mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J'}{e_0}\ldots\}}
        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}

    \inferrule* [left=]
        {  %\mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J'}\ldots\}}
        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
\end{mathpar}    
\end{comment}
